Multi sky-view\\ 3D aerosol distribution recovery

### 2013-09-22 article.tex
Several more styling corrections

%
% The cleveref package seems very cool but currently it doesn't support hebrew
% (babel) very well, so I just use if for single references.
% As a work around I redefine the number definition as suggested in:
% http://tex.stackexchange.com/questions/118235/using-the-cleveref-package-with-hebrew-and-babel
%
\usepackage[capitalise,poorman]{cleveref}
\crefname{section}{Sec.}{Secs.}
\makeatletter
\def\@@number#1{#1}
\makeatother

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}.

@@

The quality of MC increases with the number of photons launched.
\cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}[left].  A
comparison of a sample horizontal cross section is shown in
\cref{fig:mcgrid}(c).

@@

\cref{sec:simul} describes simulated scenes at various grid
resolutions.  Depending directly on the area grid finesse, $N_{\rm
  views}$ varied from 12 to 100.
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In [a,b],
    single-scattering simulated images are used as input to the
    recovery.  In [c,d], MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
We applied the reconstruction algorithm to images created as described
in \cref{sec:simul,sec:monte-carlo-simul}. We used the
L-BFGS-B algorithm~\cite{BFGS} on a computer cluster. Each core was
dedicated to rendering a modeled image. The algorithm was initialized
by ${\bm n}=0$.  Satisfactory convergence occurred in several hundred
iterations. Depending on the resolution it took between minutes to a
couple of hours to complete, in total.

>>>>

%
% The cleveref package seems very cool but currently it doesn't support hebrew
% (babel) very well, so I just use if for single references.
% As a work around I redefine the number definition as suggested in:
% http://tex.stackexchange.com/questions/118235/using-the-cleveref-package-with-hebrew-and-babel
%
\usepackage[capitalise,poorman]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\makeatletter
\def\@@number#1{#1}
\makeatother

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \Cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}.

@@

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}[left].  A
comparison of a sample horizontal cross section is shown in
\cref{fig:mcgrid}(c).

@@

\Cref{sec:simul} describes simulated scenes at various grid
resolutions.  Depending directly on the area grid finesse, $N_{\rm
  views}$ varied from 12 to 100.
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In [a,b],
    single-scattering simulated images are used as input to the
    recovery.  In [c,d], MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
We applied the reconstruction algorithm to images created as described
in \cref{sec:simul,sec:monte-carlo-simul}. We used the
L-BFGS-B algorithm~\cite{BFGS} on a computer cluster. Each core was
dedicated to rendering a modeled image. The algorithm was initialized
by ${\bm n}=0$.  Satisfactory convergence occurred in several hundred
iterations. Depending on the resolution it took between minutes to a
couple of hours to complete, in total.
